---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# geodaData

<!-- badges: start -->
<!-- badges: end -->

The goal of geodaData is to store sample spatial datasets. These datasets are intended to be used to teach basic spatial analysis concepts. They are used in the weekly R Spatial Workshop at the Center for Spatial Data Science at UChicago, and are based off of the [GeoDa workbook](https://geodacenter.github.io/documentation.html) and [data site](https://geodacenter.github.io/data-and-lab/) developed by Luc Anselin and team. Datasets are stored in the sf spatial object format.

## Installation

You can install geodaData from CRAN with:

``` r
install.packages("geodaData")
```

You can install the development version of geodaData from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("spatialanalysis/geodaData")
```
## Usage

To use geodaData in a workshop, first load `sf`, then load the package: 

```{r load}
library(sf) # can use without sf, but datasets will print weirdly in console
library(geodaData)
```

Find a list of all datasets in geodaData with:

```{r all}
data(package = "geodaData")
```

You can load a specific dataset into your R environment and show the metadata for it:

```{r data}
head(nyc)
?nyc
```

Instructions for adding a new dataset to this package can be found in the [Wiki](https://github.com/spatialanalysis/geodaData/wiki/How-to-add-a-dataset-to-this-package) of this repository.

## Datasets 

Current datasets included in this package:

-	`abandonedcars`:	Abandoned Vehicles (2016).
-	`airbnb`:	Airbnb rentals, socioeconomics, and crime in Chicago.
-	`atlanta_homicide`:	Atlanta, GA region homicide counts and rates.
-	`baltimore_home`:	Baltimore house sales prices and hedonics.
-	`bostonhsg`:	Boston housing and neighborhood data.
-	`buenosaires`:	Electoral Data for 1999 Argentinean Elections.
-	`charleston1`:	2000 Census Tract Data for Charleston, SC MSA and counties.
-	`charleston2`:	1998 and 2001 Zip Code Business Patterns (Census Bureau) in Charleston, SC MSA.
-	`chigroceries`:	Chicago supermarkets (2015).
-	`chihealth`:	Chicago Health and Socio-Economics (2014).
-	`chilelabor`:	Labor Markets in Chile (1982-2002).
-	`chisociohealth`:	Chicago Health Indicators (2005-11).
-	`cincinnati`:	Cincinnati Crime and Socio-Demographics (2008).
-	`cleveland`:	Cleveland Home Sales (2015).
-	`columbus`:	Columbus neighborhood crime (1980).
-	`commpop`:	Chicago Population Change (2000-2010).
-	`denver`:	Demographics and housing in Denver neighborhoods (2010).
-	`elections1216`:	2012 and 2016 Presidential Elections in the United States.
-	`grid100`:	Grids with simulated variables.
-	`guerry`:	Guerry "Moral Statistics" (1830s).
-	`healthplus`:	Health, Income and Diversity for US counties (2000).
-	`hickory1`:	Census Tract Data for Hickory, NC MSA and counties (2000).
-	`hickory2`:	Zip Code Business Patterns (Census Bureau) for Hickory, NC MSA (1998 and 2001).
-	`houstonhom`:	Houston, TX region homicide counts and rates (1980s-90s).
-	`juvenile`:	Cardiff juvenile delinquent residences.
-	`kchomesale`:	Home Sales in King County, WA (2014-15).
-	`lansing1`:	2000 Census Tract Data for Lansing, MI MSA and counties.
-	`lansing2`:	1998 and 2001 Zip Code Business Patterns (Census Bureau) for Lansing, MI MSA.
-	`laozone`:	Ozone measures at monitoring stations in Los Angeles basin (1996).
-	`lasrosas1`:	Corn yield, fertilizer and field data for precision agriculture, Argentina (1999).
-	`lasrosas2`:	Corn yield, fertilizer and field data for precision agriculture, Argentina (1999).
-	`liquorstore`:	Chicago Liquor Stores (2015).
-	`malaria_col_dept`:	Malaria incidence and population (1973, 95, 93 censuses and projections until 2005).
-	`malaria_col_munic`:	Malaria incidence and population (1973, 95, 93 censuses and projections until 2005).
-	`milwaukee1`:	2000 Census Tract Data for Milwaukee, WI MSA..
-	`milwaukee2`:	1998 and 2001 Zip Code Business Patterns (Census Bureau) for Milwaukee, WI MSA.
-	`mspolice`:	Police expenditures Mississippi counties.
-	`ncovr`:	Homicides & Socio-Economics (1960-90).
-	`ndvi`:	Normalized Difference Vegetation Index grid.
-	`nepal`:	Health, poverty and education indicators for Nepal districts (2007-14).
-	`nyc`:	Rental Housing and Demographics in NYC (2000s), non-spatial.
-	`nyc_sf`:	Rental Housing and Demographics in NYC (2000s).
-	`nycearnings`:	Block-level Earnings in NYC (2002-14).
-	`nyceducation`:	NYC Education (2000).
-	`nycneighborhood`:	Demographics for New York City neighborhoods (2000s).
-	`nycsociodemo`:	NYC Education and Socio-Demographics (2000s).
-	`ohio_lung`:	Ohio Lung Cancer Mortality (1960s-80s).
-	`orlando1`:	2000 Census Tract Data for Orlando, FL MSA and counties.
-	`orlando2`:	1998 and 2001 Zip Code Business Patterns (Census Bureau) for Orlando, FL MSA.
-	`ozone9799`:	Monthly ozone data, 1997-99.
-	`phoenixACS`:	Phoenix American Community Survey Data (2010, 5-year averages).
-	`pittsburghom`:	Pittsburgh homicide locations (1993).
-	`sacramento1`:	2000 Census Tract Data for Sacramento MSA.
-	`sacramento2`:	1998 and 2001 Zip Code Business Patterns (Census Bureau) for Sacramento MSA.
-	`savannah1`:	2000 Census Tract Data for Savannah, GA MSA and counties.
-	`savannah2`:	1998 and 2001 Zip Code Business Patterns (Census Bureau) for Savannah, GA MSA.
-	`scotlip`:	Male lip cancer in Scotland, 1975-80.
-	`seattle1`:	2000 Census Tract Data for Seattle, WA MSA and counties.
-	`seattle2`:	1998 and 2001 Zip Code Business Patterns (Census Bureau) for Seattle, WA MSA.
-	`Sfcartheft`:	Car theft incidents in San Francisco (points and area) - for CAST (July-Dec 2012).
-	`Sfcrime`:	Crime incidents in San Francisco (points and area) - for CAST (July-Dec 2012).
-	`Sfdrugs`:	Drug incidents in San Francisco (points and area) - for CAST (July-Dec 2012).
-	`Sfrobbery`:	Robbery incidents in San Francisco (points and area) - for CAST (July-Dec 2012).
-	`Sfvandalism`:	Vandalism incidents in San Francisco (points and area) - for CAST (July-Dec 2012).
-	`SIDS`:	North Carolina county SIDS death counts (1970s and 1980s).
- `snow`: John Snow & the 19th Century Cholera Epidemic.
-	`southom`:	US Southern county homicides 1960-1990.
-	`stlouishom`:	St Louis region county homicide counts and rates (1980s and 1990s).
-	`tampa`:	2000 Census Tract Data for Tampa, FL MSA and counties.
-	`us_sdoh`:	US Social Determinants of Health Data (2014).
- `vehicle_pts`: Point locations of abandoned vehicles in Chicago in September 2016.

## Similar Packages

Interested in finding more R packages with spatial data included? Check out:

- [spData](https://github.com/Nowosad/spData): package with large variety of
spatial datasets, accompanies the [Geocomputation with R](https://geocompr.github.io) book.
- [tidycensus](https://github.com/walkerke/tidycensus) / [tigris](https://github.com/walkerke/tigris): API package for US Census data
