---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# geodaData

<!-- badges: start -->
<!-- badges: end -->

The goal of geodaData is to store sample spatial datasets. These datasets are intended to be used to teach basic spatial analysis concepts. They are used in the weekly R Spatial Workshop at the Center for Spatial Data Science at UChicago, and are based off of the [GeoDa workbook](https://geodacenter.github.io/documentation.html) and [data site](https://geodacenter.github.io/data-and-lab/) developed by Luc Anselin and team. Datasets are stored in the sf spatial object format.

## Installation

You can install the development version of geodaData from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("spatialanalysis/geodaData")
```
## Usage

To use geodaData in a workshop, first load `sf`, then load the package: 

```{r load}
library(sf) # can use without sf, but datasets will print weirdly in console
library(geodaData)
```

Find a list of all datasets in geodaData with:

```{r all}
data(package = "geodaData")
```

You can load a specific dataset into your R environment and show the metadata for it:

```{r data}
head(nyc)
?nyc
```

Instructions for adding a new dataset to this package can be found in the [Wiki](wiki/How-to-add-a-dataset-to-this-package) of this repository.

## Datasets 

Current datasets included in this package:

- `chicago_comm`:            Chicago Community Areas (2010).
- `clev_pts`:                Cleveland Home Sales (2015).
- `commpop`:                 Chicago Population Change (2000-2010).
- `guerry`:                  Guerry "Moral Statistics" (1830s).
- `ncovr`:                   Homicides & Socio-Economics (1960-90).
- `nyc`:                     Rental Housing and Demographics in NYC (2000s),
                        non-spatial.
- `nyc_sf`:                  Rental Housing and Demographics in NYC (2000s).
- `ohio_lung`:               Ohio Lung Cancer Mortality (1960s-80s).
- `vehicle_pts`:             Abandoned Vehicles (2016).

## Similar Packages

Interested in finding more R packages with spatial data included? Check out:

- [spData](https://github.com/Nowosad/spData): package with large variety of
spatial datasets, accompanies the [Geocomputation with R](https://geocompr.github.io) book.
- [tidycensus](https://github.com/walkerke/tidycensus) / [tigris](https://github.com/walkerke/tigris): API package for US Census data
