---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# geodaData

<!-- badges: start -->
<!-- badges: end -->

The goal of geodaData is to store sample spatial datasets. These datasets are intended to be used to teach basic spatial analysis concepts. They are used in the weekly R Spatial Workshop at the Center for Spatial Data Science at UChicago, and are based off of the [GeoDa workbook](https://geodacenter.github.io/documentation.html) and [data site](https://geodacenter.github.io/data-and-lab/) developed by Luc Anselin and team. 

## Installation

You can install the development version of geodaData from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("spatialanalysis/geodaData")
```
## Example

To use geodaData in a workshop, first load the package: 

```{r load, eval=FALSE}
library(geodaData)
```

You will then be able to use the data in the package with a data() call, similar to datasets included in base R.

```{r data, eval=FALSE}
data("nyc")
```

## Similar Packages

Interested in finding more R packages with spatial data included? Check out:

- [spData](https://github.com/Nowosad/spData): package with large variety of
spatial datasets, accompanies the [Geocomputation with R](https://geocompr.github.io) book.
- [tidycensus](https://github.com/walkerke/tidycensus) / [tigris](https://github.com/walkerke/tigris): API package for US Census data
